---
title: "Tables and Figures for *Mediational E-values: Approximate Sensitivity Analysis for Unmeasured Mediator-Outcome Confounding*"
output:
  pdf_document
---
```{r setup, include = FALSE}
if (!require("drake")) {install.packages("drake"); library(drake)}
if (!require("xtable")) {install.packages("xtable"); library(xtable)}
if (!require("ggplot2")) {install.packages("ggplot2"); library(ggplot2)}
if (!require("captioner")) {install.packages("captioner"); library(captioner)}
if (!require("knitr")) install.packages("knitr")

knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  fig.align = "center"
)

loadd(vals_4_rmd)

table_nums <- captioner(prefix = "Table")

table_nums(name = "overall_res")

table_nums(name = "quant_rat_any")

table_nums(name = "bias_add")

figure_nums <- captioner(prefix = "Figure")

figure_nums(name = "compare_corrected")

figure_nums(name = "residual_bias")
```

\begin{singlespace}`r table_nums("overall_res")`\end{singlespace}
```{r results = "asis"}
do.call(print, readd(table1))
```

\begin{singlespace}`r figure_nums("compare_corrected")`\end{singlespace}
```{r fig.height = 4, fig.width = 9}
print(readd(compare_correctedA))
```
```{r fig.height = 4, fig.width = 9}
print(readd(compare_correctedB))
```
```{r fig.height = 4, fig.width = 9}
print(readd(compare_correctedC))
```
```{r fig.height = 4, fig.width = 9}
print(readd(compare_correctedD))
```

\begin{singlespace}`r table_nums("quant_rat_any")`\end{singlespace}
`r table_nums("quant_rat_any", display = "cite")`A. Probabilities drawn from uniform distribution
```{r results = "asis"}
do.call(print, readd(table2a))
```
`r table_nums("quant_rat_any", display = "cite")`B. Uniform probabilities; restricted to no qualitative interactions
```{r results = "asis"}
do.call(print, readd(table2b))
```
`r table_nums("quant_rat_any", display = "cite")`C. Log-linear model for $M$
```{r results = "asis"}
do.call(print, readd(table2c))
```
`r table_nums("quant_rat_any", display = "cite")`D. Log-linear model, restricted to no qualitative interaction
```{r results = "asis"}
do.call(print, readd(table2d))
```

\begin{singlespace}`r figure_nums("residual_bias")`\end{singlespace}
```{r fig.height = 4, fig.width = 7.5}
print(readd(resid_plotA))
```
```{r fig.height = 4, fig.width = 7.5}
print(readd(resid_plotB))
```
```{r fig.height = 4, fig.width = 7.5}
print(readd(resid_plotC))
```
```{r fig.height = 4, fig.width = 7.5}
print(readd(resid_plotD))
```

\begin{singlespace}`r table_nums("bias_add")`\end{singlespace}
```{r results = "asis"}
do.call(print, readd(table3))
```
